Three-dimensional fluorophore orientation imaging with polarized multiview microscopy

### 2018-01-19 notes/2018-01-18-osa-abstract/abstract.tex
Jan 18 email. First 3D recons.

\title{Preparing a Manuscript for Submission to an Optical Society of America Meeting or Conference}

\author{Author name(s)}
\address{Author affiliation and full address}
\email{talonchandler@talonchandler.com}

\begin{abstract}
\LaTeX{} users preparing manuscripts for OSA meetings or conferences
should use the new \texttt{osameet2.sty} style file and should observe the
guidelines described here to adhere to
OSA requirements. Users of Bib\TeX{} may use the \texttt{osajnl.bst}
style file, which is included in this distribution. Comments and
questions should be directed to the OSA Technical Papers Department (tel: +1 202.416.6191,  e-mail: cstech@osa.org).
\end{abstract}

\ocis{000.0000, 999.9999.}

\section{Main Text}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=8.3cm]{figs/epi/phantom.png}
\caption{Sample figure with preferred style for labeling parts.}
\end{figure}

\begin{table}[htb]
 \centering \caption{Sample Table}
\begin{tabular}{ccc}
    \hline
    One & Two & Three \\
    \hline
    Eins & Zwei & Drei \\
    Un & Deux & Trois \\
    Jeden & Dv\v{e} & T\v{r}i \\
    \hline
   \end{tabular}
    \end{table}

 No more than
three figures should generally be included in the paper.
Place figures as close as possible to where they
are mentioned in the text. No part of a figure should extend beyond text width, and text should not wrap around figures.

>>>>

\title{Three-dimensional fluorophore orientation imaging with polarized multiview microscopy}

\author{Talon Chandler, Min Guo, Hari Shroff, Rudolf Oldenbourg, Patrick J. La Rivi\`ere}
\address{Department of Radiology, University of Chicago, Chicago, Illinois 60637, USA.\\Section on High Resolution Optical Imaging, National Institute of Biomedical Imaging and Bioengineering,\\ National Institutes of Health, Bethesda, Maryland 20892, USA.\\ Bell Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Whitman Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Department of Physics, Brown University, Providence, Rhode Island 02912, USA.}
\email{*talonchandler@talonchandler.com} %% email address is required

\begin{abstract}
  We show that polarized fluorescence microscopes collect data in the angular
  frequency domain. We use this result to propose and demonstrate efficient
  algorithms for reconstructing three-dimensional fluorophore orientations from
  polarized multiview microscope data.
\end{abstract}

\ocis{180.2520 Fluorescence microscopy, 260.5430 Polarization}

\section{Introduction}
\section{Theory}
\section{Results}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=17cm]{figs/asym_dispim/data.pdf}
\caption{Sample figure with preferred style for labeling parts.}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=17cm]{figs/asym_dispim/recon.pdf}
\caption{Sample figure with preferred style for labeling parts.}
\end{figure}
